### 2018-04-13 paper/evaluation.tex
pass

% describe benchmarks:
We evaluated \sys and \duality on 4,309 CHC systems generated from
programs in the SV-COMP 2015~\cite{svcomp15} verification benchmark
suite.
%
To generate CHC systems, we ran the \seahorn~\cite{gurfinkel15}
verification framework with its default settings, set to timeout at 90
seconds.
%
We used the benchmarks in SV-COMP 2015~\cite{svcomp15} because they
were used to evaluate \duality in previous work~\cite{mcmillan14}.

>>>>

% describe benchmarks:
We evaluated \sys and \duality on 4,309 CHC systems generated from
programs in the SV-COMP 2015~\cite{svcomp15} verification benchmark
suite.
%
To generate CHC systems, we ran the \seahorn~\cite{gurfinkel15}
verification framework with its default settings (procedures are not
inlined and each loop-free fragment is a clause), set to timeout at 90
seconds.
%
We used the benchmarks in SV-COMP 2015~\cite{svcomp15} because they
were used to evaluate \duality in previous work~\cite{mcmillan14}.

### 2018-04-13 paper/overview.tex
pass

%first introduce the question
In \autoref{sec:running-ex}, we describe a recursion-free CHC system,
$\mcchc$ (\autoref{fig:chc}), that models the safety of program \cc{dblAbs} (\autoref{fig:multicall-code}).
%
In \autoref{sec:solve-ex}, we show that $\mcchc$ is a CDD system and
how \sys can solve it by encoding it into binary interpolants.
%
In \autoref{sec:not-in}, we illustrate that $\mcchc$ is not in
directly solvable classes introduced in previous work.
%

>>>>

%first introduce the question
In \autoref{sec:running-ex}, we describe a recursion-free CHC system,
$\mcchc$ (\autoref{fig:chc}), that models the safety of the program
\cc{dblAbs} (\autoref{fig:multicall-code}).
%
In \autoref{sec:solve-ex}, we show that $\mcchc$ is a CDD system and
how \sys can solve it by encoding it into binary interpolants.
%
In \autoref{sec:not-in}, we illustrate that $\mcchc$ is not in
directly solvable classes introduced in previous work.
%

### 2018-04-13 paper/related-work.tex
pass over most of correctness proof
pass

\sys is similar to the recursion free CHC approaches given above in
that it reduces the problem to solving a CHC system in a
directly-solvable class.
%
\sys is distinct in that it reduces to solving Clause-Dependent
Disjoint (CDD) systems.
%
As discussed in \autoref{sec:overview}, the class of CDD systems is a
superset of classes used by the approaches above. CDD systems can
also be solved directly.

@@

% DAG inlining:
DAG inlining attempts to generate compact verification conditions for
hierarchical programs~\cite{lal-qadeer15}.
%
\sys attempts to solve recursion-free CHC systems by attempting to
reduce them to compact CDD systems.
%
Because hierarchical programs and recursion-free CHC systems are
closely related, algorithms that operate on hierarchical programs
correspond to algorithms that operate on recursion-free Horn Clauses.
%
However, it is not apparent that such algorithms can be used directly
to synthesize solutions for recursion-free CHC systems.

>>>>

\sys is similar to the recursion-free CHC approaches given above in
that it reduces the problem to solving a CHC system in a
directly-solvable class.
%
\sys is distinct in that it reduces to solving Clause-Dependent
Disjoint (CDD) systems.
%
As discussed in \autoref{sec:overview}, the class of CDD systems is a
superset of classes used by the approaches above. CDD systems can
also be solved directly.

@@

% DAG inlining:
DAG inlining attempts to generate compact verification conditions for
hierarchical programs~\cite{lal-qadeer15}.
%
\sys attempts to solve recursion-free CHC systems by attempting to
reduce them to compact CDD systems.
%
Because hierarchical programs and recursion-free CHC systems are
closely related, algorithms that operate on hierarchical programs
correspond to algorithms that operate on recursion-free Horn Clauses.
%
However, it is not apparent that such algorithms can be used directly
to synthesize solutions.
